Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints

### 2025-03-09 TSUSC/systemModel.tex
move resources from other repos

\documentclass[journal]{IEEEtran}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{amssymb,amsmath}
\usepackage[font=small,skip=10pt]{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
\usepackage{ragged2e} 
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{array}
%\usepackage{nopageno}
\usepackage{url}
%\usepackage{hyperref}
%\usepackage{ulem}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage{color}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{hhline}
%\usepackage[pdftex]{graphicx}

% *** GRAPHICS RELATED PACKAGES1 ***
%

% more space
%\usepackage{txfonts}
\addtolength{\abovedisplayskip}{-2mm}
\addtolength{\belowdisplayskip}{-2mm}
\addtolength{\parskip}{-.15mm}
%\addtolength{\arraycolsep}{-.75mm}
\addtolength{\abovecaptionskip}{-1mm}
\addtolength{\belowcaptionskip}{-1mm}
%\renewcommand{\baselinestretch}{0.9}

\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
\graphicspath{{fig/}{../}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.jpg}
\else
\usepackage[dvips]{graphicx}
\graphicspath{{fig/}{../}}
\DeclareGraphicsExtensions{.eps}
\fi

%\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\renewcommand{\baselinestretch}{1}

\ifodd 1
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\revv}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(COMMENT: #1)}}%comment of the text
\else
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\newcommand{\be}{\begin{equation}}
	\newcommand{\ee}{\end{equation}}
\newcommand{\bee}{\begin{eqnarray}}
	\newcommand{\eee}{\end{eqnarray}}
\newcommand{\bse}{\begin{subequations}}
	\newcommand{\ese}{\end{subequations}}
%\def\bee#1\eee{\begin{align}#1\end{align}}
\newcommand{\nnb}{\nonumber}

\newtheorem{lem}{Lemma}
\newtheorem{propos}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defi}{Definition}

%in terms of practical feasibility and characterizing the maximum benefits of D2D load balancing is
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\makeatletter
\newcommand\semiHuge{\@setfontsize\semiHuge{22.52}{27.38}}
\makeatother
\begin{document}
	%\semiHuge
	\title{Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints}
	\author{\#}

	\author{Bahram Alinia, Mohammad H. Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada

		\thanks{ B. Alinia and N. Crespi are with the department of Networks and Mobile Multimedia Services (RS2M), Institut Mines-Telecom,
			Telecom SudParis, Evry, France (e-mail: bahram.alinia@telecom-sudparis.eu, noel.crespi@mines-telecom.fr).

			M. H. Hajiesmaili and E. Mallada are with the Department of Electrical and Computer Engineering, Johns Hopkins University, Baltimore, MD, USA (e-mail: \{hajiesmaili,mallada\}@jhu.edu).

			Z. J. Lee is with the Department of Electrical Engineering, California Institute of Technology, Pasadena, CA, USA (e-mail: zlee@caltech.edu).
		} }

		\maketitle

\begin{abstract}
%			With the rapid growth of electric vehicles, their high demand charging jobs pose an immense challenge to the grid infrastructure. 
			This paper tackles online scheduling of electric vehicles (EVs) in an adaptive charging network (ACN) with local and global peak constraints. Given the aggregate charging demand of the EVs and the peak constraints of the ACN, it might be infeasible to fully charge all the EVs according to their charging demand. Two alternatives in such resource-limited scenarios are to maximize the social welfare by partially charging the EVs (fractional model) or selecting a subset of  EVs and fully charge them (integral model). 
%			This paper tackles both fractional and integral models. 
			The critical challenge is the need for online solution design since in practical scenario\revv{s} the scheduler has no information of future arrivals of EVs in a time-coupled underlying problem. 
			For the fractional model, we devise both offline and online algorithms. We prove that the offline algorithm is optimal. Using competitive ratio as the performance measure, we prove the online algorithm achieves a competitive ratio of 2. The integral model, however, is more challenging since the underlying problem is NP-hard due to 0/1 selection criteria of EVs. Hence, efficient solution design is challenging even in offline setting. We devise a low-complexity primal-dual scheduling algorithm that achieves a bounded approximation ratio. Built upon the offline approximate algorithm, we propose an online algorithm and analyze its competitive ratio in special cases. Extensive trace-driven experimental results show that the performance of the proposed online algorithms is close to the offline optimum, and outperform the existing solutions. 
%			\rev{In particular, the grid and electricity providers should be aware of the electricity peak.	It is known in electricity market that the spot price is a dominating factor in billing cost. Hence, the utility companies need to identify a global peak constraint for the cost management purpose. This paper studies the online EV charging scheduling problem in a utility that offers EV charging service in a set of CSs, each of which having limited output power (referred to as local peak constraint) while taking into account the global peak constraint. The scheduling problem in this scenario comes with unique challenges that is not tackled previously.}

%			\rev{The problem objective is to maximize total revenue of the CSs.}

\end{abstract}
		\begin{IEEEkeywords}
			Electric Vehicle, Online Scheduling, Approximation Algorithm, Competitive Analysis
		\end{IEEEkeywords}

		\section{Introduction}
\label{sec:intro}	
%		\IEEEPARstart{A}{s} 
%		a result of global warming and environmental concerns through dependence on fossil fuels, there has been a rapid proliferation in deploying renewable energy sources. 
\IEEEPARstart{T}{o} promote quick adoption of renewable energy sources, electrification of vehicles is a trend that has been globally advocated in recent years. \rev{According to a Bloomberg report, EVs will account for more than half of the new car sales by $2040$~\cite{bloomberg}. 		
	%the global sale of EVs increased by $80\%$ in $2015$~\cite{EVSales}.
	%		With the significant advantage of electric vehicles (EVs) in being an environment friendly product, the global interest for EVs is rapidly growing, such that  
	Consequently, it is expected that demand from EV charging will constitute a considerable portion of total demand. 
	Currently, transportation consumes $29\%$ of total energy in the US, while electricity production consumes $40\%$~\cite{Zhao}.} 
%Vehicles seen accounting for 5\% of electricity use by $2040$~\cite{EVSales2}}
%%%\revv{\sout{Hence, rapid electrification of the vehicles makes the total electricity demand of EVs significant.}}

\revv{EV charging demand is a typical example of a deferrable load, and there is often considerable flexibility in the charging schedule. This property makes the problem of EV charging scheduling  important and there is an extensive research along this direction in the literature (see the recent survey~\cite{mukherjee2015review}, and references therein). In most of the existing works, the EV charging demand is treated as a constraint to the problem in a low-load regime~\cite{Tang}.  Motivated by rapid proliferation of EVs, this work tackles the EV scheduling in high-load regime, where given the aggregate charging demand of the EVs and the peak constraints of the charging network, it is not feasible to fully charge all the EVs according to their charging demand.}
%		\subsection{Microgrid: Definition, Potentials, and Challenges}
%		\label{sec:introA}
%		A common trend in the smart grid era is to install renewable energy sources in distributed manner. More specifically, medium or large commercial and industrial  customers such as universities, headquarters, etc.,  can take control of their own energy consumption by local deployment of renewable sources~\cite{Hajiesmaili2016Online}. In this setting, the residual demand, i.e., total demand subtracted by the local renewable supply, can be acquired from the external grid.

%		In addition to clean energy production, the owner of microgrid also enjoys more power sustainability and reliability, and the ability to proactively manage the energy costs.

More specifically, this paper studies resource-constrained EV charging scheduling in an adaptive charging network (ACN) governed by a single operator in a campus-scale location such as a university, a headquarter\rev{s}, etc. \cite{wu2017two}. 
\rev{A notable example is the Caltech ACN~\cite{lee2016adaptive} where individual charging ports are organized into several \textit{charging stations} (CSs) which are dispersed in a \textit{charging network}} with the capability of adaptive charging of the EVs. 
The problem is different from EV charging scheduling \revv{with capacity constraint} in single station scenarios~\cite{Tang,Wen,Shroff2014,WTang,Chen,Xiang,Zhao,Robu} (we refer to~Section~\ref{sec:rel} for detailed discussions on related work), because of the essential need to respect the aggregate peak demand of the ACN. \revv{Note that, the ACN operator might limit the total power drawn from EVs to control costs~\cite{PeakPrice,Zhang2015eEnergy}, reserve the capacity for other loads, and/or participate in demand-response programs.}
%		The EV charging loads are usually flexible and deferrable, which means that their load can be scheduled~\cite{moghaddam2017smart,DWang} to shape the total demand over time. 
%The aim of this paper is to use the deferrable property of EVs and schedule their charging jobs, so as to \rev{maximize the revenue of the ACN}.	
%		We refer to Section~\ref{sec:rel} for the literature review.

%		In particular, real-world pricing scheme for large customers is usually a hybrid time-of-use and peak-based charging model where the peak demand can significantly impact the total energy cost, e.g., the peak price is often more than $100$ times higher than the spot price~\cite{PeakPrice,Zhang2015eEnergy}. Considering total aggregate demand, the peak charge portion could be as large as $20\%-80\%$ of total cost~\cite{Xu2014Reducing}. Consequently, a substantial cost reduction could be achieved if the total peak-demand can be proactively controlled \cite{liao2015dispatch}.

%		\subsection{EV Charging Scheduling in the ACN}
%		With the proliferation of EVs, the charging requirement of the microgrid EVs could be a portion of total microgrid electricity demand.

%		To respond the electricity demand of EVs, CSs are being used where EVs can recourse to charge their battery \cite{He,liao2015dispatch,Tang}. There can be few to many CSs dispersed in an ACN, e.g., each for a parking garage of a building in a university campus. In this scenario, all parking stations are governed by a facility operator and a \textit{global} peak demand constraint is determined such that the aggregate charging demand in the entire network is less than this global peak demand \cite{DWang,Hoog}.

%		The charging scheduling of the EVs with the goal of respecting the \textit{global aggregate peak constraint}, however, is a unique problem which is different from the single station EV charging scheduling. Most of the existing work in the literature, tackle the problem in the single parking station scenario. We refer to Section~\ref{sec:rel} for in-depth discussion. As discussed in Section \ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems. 
%		On the other hand, there are only a few studies that provide global optimal solution for charging scheduling of EVs \cite{He, Moradijoz, Malhotra,Zeng,Shaaban,DWang}. Despite elegant results, the underlying problems, e.g., charging cost minimization problem in \cite{He}, average operating cost minimization with optimal electricity exchange capacity problem in \cite{DWang}, optimal station capacity problem in~\cite{Moradijoz}, user convenience maximization problem in~\cite{Malhotra}, joint optimization of system profit and user experience in~\cite{Shaaban,Zeng} are different from the problem studied in this paper.

%		\subsection{Problem, Challenges, and Contributions}
We consider a scenario with multiple EVs where each EV has different charging profile in terms of availability, charging demand, charging rate limit, and valuation of getting charged \revv{(for details see Section~\ref{sec:ev})}. We formulate an online EV charging scheduling problem with the goal of \textit{selecting} and \textit{scheduling} a subset of EVs such that: (1) the charging demand of the selected EVs are (fully or partially) satisfied; (2) the charging rate limit of EV batteries are respected, (3) the global peak constraint of the ACN is satisfied~\cite{lee2016adaptive}; (4) the local peak constraint of each CS is respected;  and finally, (5) the total revenue obtained by the valuation of the EVs is maximized.

%		of maximizing the revenue of the ACN. The constraints are the \textit{local} peak constraint of each CS, and the \textit{global} peak constraint that limits the accumulative charging demand drawn from the entire network of stations (decided by the administration of the ACN to control total peak demand~\cite{lee2016adaptive}).

There are two main challenges in the design and implementation of scheduling algorithms for EVs satisfying the goals mentioned above. \rev{Firstly, the problem calls for online scheduling design.} In practice, EVs arrive to the CS in online fashion and the scheduler has no information about the arrival and demand of the future EVs. Secondly, the underlying optimization problem in integral model is NP-hard even in offline case \rev{(see Section~\ref{sec:integral})}. This is because the problem is a mixed integer linear problem and a ``time-expanded'' extension of knapsack problem which is known as a classic NP-hard problem. In this paper, we tackle the challenge of online design by following competitive algorithm design~\cite{borodin2005online} and the challenge of NP-hardness by pursuing approximation algorithm design~\cite{approx} and make the following contributions:

$\vartriangleright$ We first consider a \textit{fractional model} (where EVs can be charged partially and the revenue is proportional accordingly) and design an optimal offline scheduling algorithm. 
%In addition to provide efficient result, the algorithm has a further elegant step to apply a valley filling strategy to further reduce the peak demand of EV charging without degrading total revenue. 
We then develop an efficient online algorithm in which no exact or stochastic information about the future EV arrivals is given. Despite its simplicity, the algorithm is proved to be $2$-competitive with optimal offline solution, i.e., the revenue of the proposed online algorithm is at least $1/2$ of the offline optimum, regardless of input sequence. 
Even though there are competitive algorithms in the literature for similar problems, to the best of our knowledge, our algorithm is the first $2$-competitive algorithm \rev{which considers the} charging rate limits.

$\vartriangleright$ We next study \rev{the} more challenging scenario of \rev{the} \textit{integral model}\rev{, }where EVs must receive all their demand to make revenue. We first propose a polynomial-time primal-dual offline approximate algorithm. We analyze the approximation ratio of the algorithm and by strengthening the linear relaxed version of the mixed integer problem~\cite{Carr}, we obtain an approximation ratio of $\alpha =1+\sum_{j=1}^m {\frac{p_j}{p_j-q_j}}.\frac{s}{s-1}$, where $p_j$ is local peak constraint in station $j$, $q_j$ is the maximum charging rate of the EVs in station $j$ and $s$ is a slackness parameter. We highlight that when $p_j \gg q_j$ and $s$ is \rev{large} enough, then $\alpha \approx m+1$, where $m$ is the number of stations in the ACN. Built on the basis of the offline algorithm, we devise an online algorithm, and discuss its competitive ratio in special cases. 
%In particular, the competitive ratio is $b\Big(1+\frac{p_j}{p_j-q_j}\cdot\frac{s}{s-1}\Big)$ for single station scenario, where $b$ is the number of batches with the same arrival time.

$\vartriangleright$ We conduct a set of  simulations to evaluate the performance of our proposed algorithms. 
%For offline scheduling problem under integral charging model, the results  demonstrate that the proposed approximation algorithm is close to the optimal solution and is significantly better than the obtained theoretical bounds. 
The results of online algorithms for both integral and fractional settings are close to the optimum (within $90\%$ and $94\%$ for integral and fractional models in a representative scenario). In addition, our algorithm outperforms the existing scheduling algorithm in Caltech ACN~\cite{lee2016adaptive} by $35\%$ for integral revenue model.
%The simulation section also discusses on the positive and negative effects of slackness parameter in different scenarios.

%To the best of our knowledge, this problem is not addressed yet in previous studies.

%		\subsection{Paper Organization}
%		The rest of this paper is organized as follows. Section~\ref{sec:rel} reviews the literature. In Section \ref{sec:model}, the system model  and problem formulation are described. 
%		Section \ref{sec:fractional} provides offline and online algorithms for fractional model. We study integral model in Section \ref{sec:integral} and propose online and offline algorithms. The simulation results are reported in Section~\ref{sec:simul}. Section~\ref{sec:conclusion} concludes the paper and highlights future directions.

\section{Related Work}
\label{sec:rel}
\revv{There is an extensive work in the general topic of EV demand management and scheduling~\cite{mukherjee2015review} by considering different scenarios such as optimal operations with EV coordinations~\cite{mukherjee2017distributed}, EV scheduling with incorporation of renewable energy, and energy storage systems~\cite{de2017impact,shafie2018innovative}. In this section, we focus on the literature related to peak-constrained EV charging scheduling in single and multiple stations.}
\subsubsection{Peak-Constrained EV Charging Scheduling}
\label{sec:rel:peakconstrained}			
\revv{There is an extensive literature on EV charging scheduling problem focusing on single CS~\cite{Tang,Wen}, while the local and global peak constraints are omitted or only the local peak is considered.}	As we discuss in Section~\ref{sec:problem}, the global optimal solution cannot be obtained by separately solving the single station problems. Hence, those solutions cannot be directly applied to the multiple CS scenario with global peak constraints.

%A scenario that local and global peak constraints exist is the case that scheduling is required for a charging network for multiple CSs. 
Studies in \cite{He,malhotra2017distributed,Moradijoz,DWang,Zeng,Shaaban} tackled charging scheduling problem in multiple CSs. The authors in~\cite{He} studied a global cost minimization EV charging scheduling problem. However, there is no limit on the maximum peak demand that the system can tolerate. Consequently, the peak can be arbitrary high and beyond the physical limit of the transformers in the charging station~\cite{lee2016adaptive} leading to huge electricity bills~\cite{Zhang2015eEnergy}. Besides, the charger devices installed in the CSs have limitation on the maximum power that they can transfer in each time unit~\cite{Tesla}. 
%We solve the issue by constraining local and global peaks. However, to meet the peak constraints, it may not be feasible to respond to all charging demands. Consequently, only a subset of EVs can be charged~\cite{Xiang}, which is captured in our problem formulation. 
\cite{DWang} considered a multi-microgrid system with global peak constraint where each microgrid has a CS and the goal is to manage electricity exchange between microgrids and main grid to minimize the operating costs. The authors assume that required information about individual EVs is available by forecast which may not represent a real scenario. A similar assumption is made in \cite{Zeng,Shaaban} where the objective is to maximize total utility of EVs and aggregators in a distribution network.
%\rev{To be removed: In our solution, we applied a priority based selection process (based on the EVs' valuation) to respond to the demands to make sure that total peak respects the constraints. The selection process can be made based on different criteria such as the value of each charging request \cite{Lee, Xiang} or the priority.}
%To avoid big billing cost in peak hours, \cite{Moradijoz} proposed a solution based on genetic algorithm to find optimal capacity and location of parking lots for serving demands in peak hours with the goal of maximizing total benefit of all stations. Although authors studied the problem under multiple CS setting, their solution is not applicable to our setting when the CSs are already set up. 
The authors in~\cite{malhotra2017distributed} use a similar model as in this paper, where both local and global peak constraints are considered. However, the authors solve the single-slot problem, which fails to provide a general solution taking into account EVs' arrival and departure times as considered in our study.
Finally, as an alternative approach to control the peak, some studies directly target minimizing the peak~\cite{Zhao, Karfopoulos}. In~\cite{Zhao}, an online algorithm is developed for EV charging to minimize the peak and \cite{Karfopoulos} proposed a valley filling method by leveraging V2G in peak hours. Although the peak is minimized in above works, it cannot guarantee that the minimized peak is tolerable by the underlying charging network.

\subsubsection{Scheduling Under Demand Uncertainty}
A main challenge in EV scheduling problem is to cope with demand uncertainty. Many studies including \cite{Shroff2014,Tang,WTang,Chen,Xiang,Zhao,Robu} addressed online scheduling problem with different objectives. \cite{Shroff2014,Xiang} studied the problem of maximizing social welfare considering the benefit for both users and service provider. \cite{Tang} and \cite{WTang} developed algorithms to minimize the charging price for the CS, where the proposed algorithm in \cite{Tang} is $2.39$-competitive. 
%An online algorithm developed in \cite{Chen} to optimize overall operating profit of the service provider. 
In \cite{Robu}, an online $2$-competitive algorithm is proposed for a single CS, assuming that EVs are capable of being discharged in a negligible amount of time. The assumption, however, is not realistic for EVs.

Our problem in this paper is unique from above works in many respects. First, we study the problem in an ACN where several CSs exist, while none of the above studies solve the problem under this setting. Second, the previous algorithms do not work for both integral and fractional charging models. In addition, \cite{WTang,Chen} put no limit on the charging rate of EVs which makes their solution impractical in real scenarios. Also, \cite{WTang,Tang, Shroff2014,Chen,Zhao} do not consider the peak limit of the CS. 
\revv{Note that some studies~\cite{jin2017optimal} tackle the scenarios of satisfying the large demands (possibly EV demands) by participating in electricity market. This study assumes that the electricity price is given and fixed, and leaves the case of real-time pricing as the future direction. In addition, there are studies that incorporate prediction in online EV charging scheduling~\cite{wang2017predictive,chen2014distributional}. The prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction. Deviation from prediction models, however, degrades their performance. Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.} 
\revv{Finally, in~\cite{Alinia2018ITS}, we considered a simplified EV charging scheduling in fractional model without global peak constraints and devised heuristic algorithms (without competitive and approximation analysis) with on-arrival commitment for EVs to notify the amount that they can receive by their departure. }
%In this paper, we consider these limitations and develop online and offline algorithms for fractional and integral revenue models in an ACN and provide theoretical bounds on their performance.

%It is important to note that there is a considerable similarity between EV scheduling problem and classical job scheduling problem \cite{}. However, most algorithm developed for job scheduling problem  do not consider a limit on processing rate of the jobs.

%\cite{Shroff2014} and \cite{Stein2012} study social welfare maximization problem while the profit of both EV owners and CS is considered.  social welfare of the EV owners \cite{Stein2012}, charging cost \cite{Tang,WTang}, and total value of fully charged EVs \cite{Azar}). In addition, \cite{WTang, Tang,Shroff2014,Zhao} do not take into account the peak limitation of CS. }
		\section{System Model and Problem Formulation}
		\label{sec:model}

		\subsection{System Model}
		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
\subsubsection{Charging Network}
\label{sec:acn}
Our charging network model is inspired by the Caltech ACN~\cite{lee2016adaptive} as illustrated in Fig.~\ref{fig:model-a}. In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN). Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN). The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.  
%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2016adaptive}). 
In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.

We assume that there are $m$ EV switch panels that represent $m$ CSs. In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint. The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.  
%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
To increase the flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$). \rev{While this increases flexibility, it also couples the problem of EV charging scheduling across different CSs.}
%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.

@@

\begin{figure}	
\centering
\minipage{0.49\textwidth}
				\begin{subfigure}[b]{0.69\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{model-a.pdf}
						\caption{Caltech adaptive charging network (ACN)}
						\label{fig:model-a}
					\end{center}
				\end{subfigure}%
				\begin{subfigure}[b]{0.29\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{model-b.pdf}
						\caption{Communication model with server}
						\label{fig:model-b}
					\end{center}
				\end{subfigure}%  
\caption{System model \cite{lee2016adaptive}.} 
\label{fig:slackness1}
\endminipage
\end{figure}

>>>>

\section{System Model and Problem Formulation}
		\label{sec:model}

		\subsection{System Model}
		We consider a time-slotted system model in which the time horizon is divided to $T$ equal length slots ${t=\{1, 2, \dots ,T\}}$ (e.g., $T=24$ with time slots of $1$ hour length).
\subsubsection{Charging Network}
\label{sec:acn}
Our charging network model is inspired by the Caltech ACN~\cite{lee2018adaptive} as illustrated in Fig.~\ref{fig:model-a}. In \rev{the} Caltech EV charging network (located in a parking garage), electricity is distributed through a two-level transformer architecture from a main switch panel to multiple EV switch panels (\rev{$2$} panels in the current Caltech ACN). Each EV switch panel then is connected to several chargers ($\approx$25 chargers \rev{per panel} in the Caltech ACN). The total power drawn from the main switch panel \rev{by} the charging network has a power limit of  $p^\mathsf{total}$, that is determined by the facility operator to control the costs, reserve the capacity for other loads, and/or participate in demand-response programs.  
%This power, where we refer to it as \emph{network power limit} is used for both EV charging as well as non-EV charging purposes (e.g., lighting, fans, etc \cite{lee2018adaptive}). 
In other words, $p^\mathsf{total}$, which we refer to it as the \textit{global peak}, hereafter, limits the maximum aggregate EV charging load at each time slot. 
%The global peak must be less than or equal to the value obtained by subtracting non-EV load from network power limit. 
%When we write \emph{global peak constraint}, it refers to $p^\mathsf{total}$.  
%$p^\mathsf{total}$ is the maximum allowed aggregated electricity consumption by all stations at each slot and limits the total transferable power to EVs.

We assume that there are $m$ EV switch panels that represent $m$ CSs. In addition to the global peak constraint, each CS $j$ has \rev{a} capacity constraint on \rev{its} total power drawn, indicated by $p_j$, and referred to it as the \emph{local peak} constraint. The \rev{value of} $p_j$ is determined by the output power limit of the transformers installed between the main switch panel and EV switch panels and could be different for each EV switch panel.  
%installed chargers in a CS have limited output power to charge EVs ~\cite{Wen,Xiang,Tesla}. Therefore, for CS $j$, $p_j$ cannot be more than sum of output power of its chargers. 
\rev{It is often observed that the charging demand of different CSs (EV switch panels in Fig.~\ref{fig:model-a}) are well below the local peak constraints.}
To reduce costs by taking advantage of flexibility due to heterogeneous charging demand of CSs, in the Caltech ACN, the global peak constraint of the main switch can be \textit{over-provisioned}, i.e., $p^\mathsf{total}$ is less than the aggregate local peaks,  ($\sum_j p_j\geq p^\mathsf{total}$). \rev{While this decreases costs, it also couples the problem of EV charging scheduling across different CSs.}
%Despite increased flexibility, the over-provisioning property, however, couples the problem of EV charging scheduling across different CSs. 
Our solutions in this paper will be centralized ones which can be obtained through communication between the CSs and a central server as illustrated in Fig. \ref{fig:model-b}.

@@

\begin{figure}	
\centering
\minipage{0.49\textwidth}
				\begin{subfigure}[b]{0.69\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{model-a.png}
						\caption{Caltech adaptive charging network (ACN)}
						\label{fig:model-a}
					\end{center}
				\end{subfigure}%
				\begin{subfigure}[b]{0.29\textwidth}
					\begin{center}
						\includegraphics[width=\textwidth]{model-b.png}
						\caption{Communication model with server}
						\label{fig:model-b}
					\end{center}
				\end{subfigure}%  
\caption{System model \cite{lee2018adaptive}.} 
\label{fig:slackness1}
\endminipage
\end{figure}

		\begin{table} 
			\caption{Summary of key notations}
%			\vspace{-3mm}
			\label{tbl:not}
			\begin{center}
				\begin{tabular}{|c L{6.5cm}|}
					\hline
					\textbf{Notation} & \textbf{Description} \\
					\hline \hline			
					$T$ & Number of time slots, indexed by $t$\\			
					$m$ & Number of CSs, indexed by $j$\\			
					$n$ & Number of EVs, indexed by $i$\\			
					\hline
					\hline
					$a_i$ & Arrival time of EV $i$\\
					$d_i$ & Departure time of EV $i$\\
					$D_i$ & Demand of EV $i$\\
					$v_i$ & Valuation of EV $i$ for receiving its demand $D_i$ \\
					$k_i$ & Maximum charging rate of EV $i$\\
					$h(i)$ & CS of EV $i$\\
					\hline
					\hline
					$q_j$ & Maximum $k_i$ among all EVs in CS $j$\\
					$p_j$ & Maximum aggregate charging rate in station $j$\\
					$p^\mathsf{total}$ & Maximum aggregate charging rate of all stations\\
					\hline
					\hline
					$y_i^t$ & \textbf{opt. variable}, The amount that EV $i$ is charged at $t$ \\
					\hline
				\end{tabular}
			\end{center}
		\end{table}
		\subsubsection{EVs}
		\label{sec:ev} There are $n$ EVs in the system, indexed by $i$.
		%, all available at time $t=1$ to be charged\footnote{This assumption is reasonable for the %official buildings where the starting hour of the working day is fixed for all the %employers. Extensions to the case with different arrival times for the EVs, is part of the %future work.}. 
		EV $i$ is represented by a charging profile $\langle a_i,d_i,v_i,D_i,k_i\rangle$ 
		indicating its arrival time, departure time, willingness to pay, charging demand, and maximum charging rate, respectively. 
		%(depends on physical properties of EVs battery) 
		More specifically, the charging of EV $i$ can be scheduled within its \emph{availability window}, $[a_i,d_i]$. The charging rate at each slot is bounded by $k_i$, a parameter that depends on the physical constraints of the \rev{battery and on-board charger}. It is assumed that the charging profile of each EV is feasible with respect to its maximum charging rate and a slackness parameter $s\geq 1$, which is the minimum ratio between the park time of the EV and its minimum charging time, i.e., ${D_i\leq k_i(d_i-a_i+1)/s}$. The slackness parameter is imposed to tune the flexibility of the charging scheduling. In extreme case $s=1$,  the flexibility is minimum and the flexibility improves as $s$ increases. 
%		Note  that  the slackness  parameter  can  impact  the  total  revenue  and  is  investigated  in  simulation  experiments  in Section~\ref{sec:simul}.
		We assume that EV owners select their CS, perhaps the nearest to them, and so the assignments are given to the problem. Define $h(i)$ as the CS of EV~$i$.
		Moreover, $q_j$ denotes the maximum $k_i$ among all EVs in CS $j$, i.e., $q_j=\max_{h(i)=j} k_i$. 
		Finally, $v_i$ is the willingness to pay of EV $i$ to receive its entire demand $D_i$ before the departure time $d_i$. Note that in resource-constrained EV scheduling in ACN, it is not feasible to fulfill the entire demand of all EVs, hence, the problem turns into a resource allocation one with the goal of maximizing the aggregate value (a.k.a. utility) obtained from the EVs. In this way, each user can announce $v_i$ as its willingness to pay to get charged.
		%We assume that there is no gain for the CS if EV $i$ is partially charged.
